An Extensible Approach to Verification of Embedded Network Systems*

### 2014-04-22 tech-project/paper.tex
updating C Translation Model.

\subsection{C Translation Model}
One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each. Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source. In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations. Another such consideration includes memory, and decisions on dynamic or static allocation. RESOLVE does not currently provide specifications towards a memory model but is in aspirations of providing a dynamically allocatable system. Following suit, we will introduce a stack based memory allocator in section \#.

>>>>

\subsection{C Translation Model}
One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each. Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source. In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.

The memory model must also be considered as an additional verifiable component. Currently, RESOLVE is not capable of creating a complete specification of memory\footnote{RESOLVE is an object based language and has variable sized structures. Using dynamically allocatable memory is the favored approach to allow arbitrarily sized data.}. Thus, a memory model must be realized without a specification. To provide a straight forward translation from RESOLVE to C, we provide a dynamically-based memory allocator for use on embedded systems.
